\documentclass[twoside, openany, 12pt]{extbook}

\usepackage[top=2cm,bottom=2.5cm,left=3cm,right=3cm,headsep=14pt,letterpaper]{geometry}

% PACKAGES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../../common/packages.tex}

%-------------------------------------------------------------------------------
% Purpose: enable \onehalfspacing{} or \doublespacing{}
%-------------------------------------------------------------------------------
\usepackage{setspace}

%-------------------------------------------------------------------------------
% Purpose: change paragraphs to block style paragraphs without initial indent
%-------------------------------------------------------------------------------
\usepackage{parskip}

% COMMANDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tab}[1][0.5cm]{\hspace*{#1}}

% SETUP    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../../common/page_headers.tex}

\onehalfspacing{}
%\doublespacing{}

\raggedbottom{}

%%% TODO: Add back in
%\input{../../../sbsr/books/packages/sbsr_lesson_setup.tex}

% add hyperlinks
%\usepackage{hyperref}

%\usepackage{parskip}
%\usepackage{dirtytalk}
%\usepackage{setspace}
%\doublespacing

%\fontfamily{ttfamily}
%\selectfont

%\usepackage{amsmath}
%\newcommand{\myleftarrow}
%  {\( \leftarrow \)}

\begin{document}
\chapter{2John}

\newpage\section{The Elder}

% 2john 01:01
The elder,
\\
to the chosen lady and her children,
\\
whom I love in truth,
\\
and not I only,
\\
but also all those who know the truth,
\\
% 2john 01:02
for the truth's sake,
\\
which remains in us,
\\
and it will be with us forever:

% 2john 01:03
Grace, mercy, and peace will be with us,
\\
from God the Father and from the Lord Jesus Christ,
\\
the Son of the Father,
\\
in truth and love.

\newpage\section{I Rejoice Greatly}

% 2john 01:04
I rejoice greatly that I have found some of your children walking in truth,
\\
even as we have been commanded by the Father.

\newpage\section{Now I Beg You, Dear Lady}

% 2john 01:05
Now I beg you, dear lady,
\\
not as though I wrote to you a new commandment,
\\
but that which we had from the beginning,
\\
that we love one another.

% 2john 01:06
This is love,
\\
that we should walk according to his commandments.

This is the commandment,
\\
even as you heard from the beginning,
\\
that you should walk in it.

\newpage\section{For Many Deceivers}

% 2john 01:07
For many deceivers have gone out into the world,
\\
those who don’t confess that Jesus Christ came in the flesh.

This is the deceiver and the Antichrist.

\newpage\section{Watch Yourselves}

% 2john 01:08
Watch yourselves,
\\
that we don’t lose the things which we have accomplished,
\\
but that we receive a full reward.

\newpage\section{Whoever Transgresses}

% 2john 01:09
Whoever transgresses and doesn’t remain in the teaching of Christ doesn’t have God.

He who remains in the teaching has both the Father and the Son.

% 2john 01:10
If anyone comes to you and doesn’t bring this teaching,
\\
don’t receive him into your house,
\\
and don’t welcome him,
\\
% 2john 01:11
for he who welcomes him participates in his evil deeds.

\newpage\section{Having Many Things to Write to You}

% 2john 01:12
Having many things to write to you,
\\
I don’t want to do so with paper and ink,
\\
but I hope to come to you and to speak face to face,
\\
that our joy may be made full.

% 2john 01:13
The children of your chosen sister greet you.

Amen.
\chapter{3John}

\newpage\section{The Elder to Gaius the Beloved}

% 3john 01:01
The elder

to Gaius the beloved,
\\
\tab{}
whom I love in truth.

\newpage\section{Beloved}

% 3john 01:02
Beloved,
\\
I pray
\\
\tab{}
that you may prosper in all things
\\
\tab{}
and be healthy,
\\
\tab{}
\tab{}
even as your soul prospers.

% 3john 01:03
For I rejoiced greatly
\\
\tab{}
when brothers came
\\
\tab{}
and testified about your truth,
\\
\tab{}
\tab{}
even as you walk in truth.

% 3john 01:04
I have no greater joy than this:
\\
\tab{}
to hear about my children walking in truth.

\newpage\section{Beloved}

% 3john 01:05
Beloved,
\\
you do a faithful work
\\
\tab{}
in whatever you accomplish
\\
\tab{}
\tab{}
for those who are brothers and strangers.

% 3john 01:06
They have testified about your love
\\
\tab{}
before the assembly.

You will do well
\\
\tab{}
to send them forward
\\
\tab{}
\tab{}
on their journey
\\
\tab{}
\tab{}
\tab{}
in a way worthy of God,
\\
% 3john 01:07
because
\\
\tab{}
for the sake of the Name
\\
\tab{}
\tab{}
they went out,
\\
\tab{}
\tab{}
\tab{}
taking nothing from the Gentiles.

% 3john 01:08
We therefore ought to receive such,
\\
that we may be fellow workers
\\
\tab{}
for the truth.

\newpage\section{I Wrote to the Assembly}

% 3john 01:09
I wrote to the assembly,
\\
but Diotrephes,
\\
\tab{}
who loves to be first among them,
\\
doesn’t accept what we say.

% 3john 01:10
Therefore,
\\
if I come,
\\
I will call attention to his deeds which he does,
\\
\tab{}
unjustly accusing us with wicked words.

Not content with this,
\\
\tab{}
he doesn’t receive the brothers himself,
\\
\tab{}
and those who would,
\\
\tab{}
\tab{}
he forbids and throws out of the assembly.

\newpage\section{Beloved, Don’t Imitate That Which is Evil}

% 3john 01:11
Beloved,
\\
don’t imitate that which is evil,
\\
but that which is good.

He who does good is of God.

He who does evil hasn’t seen God.

\newpage\section{Demetrius Has the Testimony of All}

% 3john 01:12
Demetrius has the testimony of all,
\\
and of the truth itself;
\\
yes,
\\
we also testify,
\\
and you know that our testimony is true.

\newpage\section{I Had Many Things to Write to You}

% 3john 01:13
I had many things to write to you,
\\
but I am unwilling to write to you with ink and pen;
\\
% 3john 01:14
but I hope to see you soon.

Then we will speak face to face.

\newpage\section{Peace Be to You}

Peace be to you.

The friends greet you.

Greet the friends by name.
\chapter{Jude}

\newpage\section{Jude, a Servant of Jesus Christ}

% jude 01:01
Jude,
\\
a servant of Jesus Christ,
\\
and brother of James,
\\
to those who are called,
\\
sanctified by God the Father,
\\
and kept for Jesus Christ:

% jude 01:02
May mercy,
peace,
and love
\\
\tab
be multiplied to you.

\newpage\section{Beloved}

% jude 01:03
Beloved,
\\
while I was very eager
\\
\tab{}
to write
\\
\tab{}
\tab{}
to you
\\
\tab{}
\tab{}
\tab{}
about our common salvation,
\\
I was constrained
\\
\tab{}
to write
\\
\tab{}
\tab{}
to you
\\
\tab{}
\tab{}
\tab{}
exhorting you
\\
\tab{}
\tab{}
\tab{}
\tab{}
to contend earnestly
\\
\tab{}
\tab{}
\tab{}
\tab{}
\tab{}
for the faith
\\
\tab{}
\tab{}
\tab{}
\tab{}
\tab{}
\tab{}
which was once for all
delivered to the saints.

\newpage\section{For There are Certain Men}

% jude 01:04
For there are certain men who crept in secretly,
\\
even those who were long ago written about for this condemnation:
\\
\tab{}
ungodly men,
\\
\tab{}
\tab{}
turning the grace of our God into indecency,
\\
\tab{}
\tab{}
and denying our only Master,
God,
and Lord,
Jesus Christ.

\newpage\section{Now I Desire to Remind You}

% jude 01:05
Now I desire to remind you,
\\
\tab{}
though you already know this,
\\
that the Lord,
\\
\tab{}
having saved a people out of the land of Egypt,
\\
\tab{}
afterward destroyed those who didn’t believe.

\newpage\section{Angels}

% jude 01:06
Angels who didn’t keep their first domain,
\\
but deserted their own dwelling place,
\\
he has kept in everlasting bonds
\\
\tab{}
under darkness
\\
\tab{}
\tab{}
for the judgment of the great day.

%\newpage\section{Even as Sodom and Gomorrah}

% jude 01:07
Even as Sodom and Gomorrah and the cities around them,
\\
having in the same way as these
\\
\tab{}
given themselves over to sexual immorality
\\
\tab{}
and gone after strange flesh,
\\
are shown as an example,
\\
\tab{}
suffering the punishment of eternal fire.

\newpage\section{Yet in the Same Way}

% jude 01:08
Yet in the same way,
\\
these also in their dreaming
\\
\tab{}
defile the flesh,
\\
\tab{}
despise authority,
\\
\tab{}
and slander celestial beings.

% jude 01:09
But Michael,
the archangel,
\\
when contending with the devil
\\
and arguing about the body of Moses,
\\
\tab{}
dared not bring against him an abusive condemnation,
\\
but said,
\\
\tab{}
``May the Lord rebuke you!''

% jude 01:10
But these speak evil of whatever things they don’t know.

They are destroyed
\\
\tab{}
in these things
\\
\tab{}
\tab{}
that they understand naturally,
\\
like the creatures without reason.

\newpage\section{Woe to Them!}

% jude 01:11
Woe to them!

For they went in the way of Cain,
\\
and ran riotously in the error of Balaam for hire,
\\
and perished in Korah's rebellion.

\newpage\section{These are Hidden Rocky Reefs}

% jude 01:12
These are
\\
\tab{}
hidden rocky reefs
\\
\tab{}
\tab{}
in your love feasts
\\
\tab{}
\tab{}
\tab{}
when they feast with you,
\\
\tab{}
shepherds
\\
\tab{}
\tab{}
who without fear feed themselves;
\\
\tab{}
clouds
\\
\tab{}
\tab{}
without water,
\\
\tab{}
\tab{}
carried along by winds;
\\
\tab{}
autumn trees
\\
\tab{}
\tab{}
without fruit,
\\
\tab{}
\tab{}
twice dead,
\\
\tab{}
\tab{}
\tab{}
plucked up by the roots;
% jude 01:13
wild waves of the sea,
\\
\tab{}
\tab{}
foaming out their own shame;
\\
\tab{}
wandering stars,
\\
\tab{}
\tab{}
for whom the blackness of darkness
has been reserved forever.

\newpage\section{About These Also Enoch}

% jude 01:14
About these also Enoch,
\\
\tab{}
the seventh from Adam,
\\
prophesied,
saying,

{\itshape{}
  \tab{}
  Behold,
  \\
  \tab{}
  the Lord came with ten thousands of his holy ones,
  \\
  % jude 01:15
  \tab{}
  to execute judgment on all,
  \\
  \tab{}
  and to convict all the ungodly
  \\
  \tab{}
  \tab{}
  of all their works of ungodliness
  \\
  \tab{}
  \tab{}
  \tab{}
  which they have done in an ungodly way,
  \\
  \tab{}
  and of all the hard things
  \\
  \tab{}
  \tab{}
  which ungodly sinners have spoken against him.
}

% jude 01:16
These are murmurers and complainers,
\\
walking after their lusts ---
\\
\tab{}
and their mouth speaks proud things ---
\\
\tab{}
\tab{}
showing respect of persons to gain advantage.

\newpage\section{But You, Beloved}

% jude 01:17
But you, beloved,
\\
remember the words
\\
\tab{}
which have been spoken before
\\
\tab{}
\tab{}
by the apostles of our Lord Jesus Christ.

% jude 01:18
They said to you,

{\itshape{}
  \tab{}
  In the last time there will be mockers,
  \\
  \tab{}
  walking after their own ungodly lusts.
}

% jude 01:19
These are those who cause divisions and are sensual,
\\
not having the Spirit.

\newpage\section{But You, Beloved}

% jude 01:20
But you, beloved,
\\
keep building up yourselves
\\
\tab{}
on your most holy faith,
\\
praying in the Holy Spirit.

% jude 01:21
Keep yourselves in God's love,
\\
looking for the mercy of our Lord Jesus Christ
\\
\tab{}
to eternal life.

% jude 01:22
On some have compassion,
\\
\tab{}
making a distinction,
\\
% jude 01:23
and some save,
\\
\tab{}
snatching them out of the fire with fear,
\\
\tab{}
hating even the clothing stained by the flesh.

\newpage\section{Now to Him Who is Able}

% jude 01:24
Now to him who is able
\\
\tab{}
to keep them from stumbling,
\\
\tab{}
and to present you faultless
\\
\tab{}
\tab{}
before the presence of his glory
\\
\tab{}
\tab{}
\tab{}
in great joy,
\\
% jude 01:25
to God our Savior,
\\
\tab{}
who alone is wise,
\\
\tab{}
\tab{}
be glory and majesty,
\\
\tab{}
\tab{}
dominion and power,
\\
\tab{}
\tab{}
both now and forever.
\\
Amen.


\end{document}
