\chapter{Jude}

\newpage\section{Jude, a Servant of Jesus Christ}

% jude 01:01
Jude,
\\
a servant of Jesus Christ,
\\
and brother of James,
\\
to those who are called,
\\
sanctified by God the Father,
\\
and kept for Jesus Christ:

% jude 01:02
May mercy,
peace,
and love
\\
\tab
be multiplied to you.

\newpage\section{Beloved}

% jude 01:03
Beloved,
\\
while I was very eager
\\
\tab{}
to write
\\
\tab{}
\tab{}
to you
\\
\tab{}
\tab{}
\tab{}
about our common salvation,
\\
I was constrained
\\
\tab{}
to write
\\
\tab{}
\tab{}
to you
\\
\tab{}
\tab{}
\tab{}
exhorting you
\\
\tab{}
\tab{}
\tab{}
\tab{}
to contend earnestly
\\
\tab{}
\tab{}
\tab{}
\tab{}
\tab{}
for the faith
\\
\tab{}
\tab{}
\tab{}
\tab{}
\tab{}
\tab{}
which was once for all
delivered to the saints.

\newpage\section{For There are Certain Men}

% jude 01:04
For there are certain men who crept in secretly,
\\
even those who were long ago written about for this condemnation:
\\
\tab{}
ungodly men,
\\
\tab{}
\tab{}
turning the grace of our God into indecency,
\\
\tab{}
\tab{}
and denying our only Master,
God,
and Lord,
Jesus Christ.

\newpage\section{Now I Desire to Remind You}

% jude 01:05
Now I desire to remind you,
\\
\tab{}
though you already know this,
\\
that the Lord,
\\
\tab{}
having saved a people out of the land of Egypt,
\\
\tab{}
afterward destroyed those who didn’t believe.

\newpage\section{Angels}

% jude 01:06
Angels who didn’t keep their first domain,
\\
but deserted their own dwelling place,
\\
he has kept in everlasting bonds
\\
\tab{}
under darkness
\\
\tab{}
\tab{}
for the judgment of the great day.

%\newpage\section{Even as Sodom and Gomorrah}

% jude 01:07
Even as Sodom and Gomorrah and the cities around them,
\\
having in the same way as these
\\
\tab{}
given themselves over to sexual immorality
\\
\tab{}
and gone after strange flesh,
\\
are shown as an example,
\\
\tab{}
suffering the punishment of eternal fire.

\newpage\section{Yet in the Same Way}

% jude 01:08
Yet in the same way,
\\
these also in their dreaming
\\
\tab{}
defile the flesh,
\\
\tab{}
despise authority,
\\
\tab{}
and slander celestial beings.

% jude 01:09
But Michael,
the archangel,
\\
when contending with the devil
\\
and arguing about the body of Moses,
\\
\tab{}
dared not bring against him an abusive condemnation,
\\
but said,
\\
\tab{}
``May the Lord rebuke you!''

% jude 01:10
But these speak evil of whatever things they don’t know.

They are destroyed
\\
\tab{}
in these things
\\
\tab{}
\tab{}
that they understand naturally,
\\
like the creatures without reason.

\newpage\section{Woe to Them!}

% jude 01:11
Woe to them!

For they went in the way of Cain,
\\
and ran riotously in the error of Balaam for hire,
\\
and perished in Korah's rebellion.

\newpage\section{These are Hidden Rocky Reefs}

% jude 01:12
These are
\\
\tab{}
hidden rocky reefs
\\
\tab{}
\tab{}
in your love feasts
\\
\tab{}
\tab{}
\tab{}
when they feast with you,
\\
\tab{}
shepherds
\\
\tab{}
\tab{}
who without fear feed themselves;
\\
\tab{}
clouds
\\
\tab{}
\tab{}
without water,
\\
\tab{}
\tab{}
carried along by winds;
\\
\tab{}
autumn trees
\\
\tab{}
\tab{}
without fruit,
\\
\tab{}
\tab{}
twice dead,
\\
\tab{}
\tab{}
\tab{}
plucked up by the roots;
% jude 01:13
wild waves of the sea,
\\
\tab{}
\tab{}
foaming out their own shame;
\\
\tab{}
wandering stars,
\\
\tab{}
\tab{}
for whom the blackness of darkness
has been reserved forever.

\newpage\section{About These Also Enoch}

% jude 01:14
About these also Enoch,
\\
\tab{}
the seventh from Adam,
\\
prophesied,
saying,

{\itshape{}
  \tab{}
  Behold,
  \\
  \tab{}
  the Lord came with ten thousands of his holy ones,
  \\
  % jude 01:15
  \tab{}
  to execute judgment on all,
  \\
  \tab{}
  and to convict all the ungodly
  \\
  \tab{}
  \tab{}
  of all their works of ungodliness
  \\
  \tab{}
  \tab{}
  \tab{}
  which they have done in an ungodly way,
  \\
  \tab{}
  and of all the hard things
  \\
  \tab{}
  \tab{}
  which ungodly sinners have spoken against him.
}

% jude 01:16
These are murmurers and complainers,
\\
walking after their lusts ---
\\
\tab{}
and their mouth speaks proud things ---
\\
\tab{}
\tab{}
showing respect of persons to gain advantage.

\newpage\section{But You, Beloved}

% jude 01:17
But you, beloved,
\\
remember the words
\\
\tab{}
which have been spoken before
\\
\tab{}
\tab{}
by the apostles of our Lord Jesus Christ.

% jude 01:18
They said to you,

{\itshape{}
  \tab{}
  In the last time there will be mockers,
  \\
  \tab{}
  walking after their own ungodly lusts.
}

% jude 01:19
These are those who cause divisions and are sensual,
\\
not having the Spirit.

\newpage\section{But You, Beloved}

% jude 01:20
But you, beloved,
\\
keep building up yourselves
\\
\tab{}
on your most holy faith,
\\
praying in the Holy Spirit.

% jude 01:21
Keep yourselves in God's love,
\\
looking for the mercy of our Lord Jesus Christ
\\
\tab{}
to eternal life.

% jude 01:22
On some have compassion,
\\
\tab{}
making a distinction,
\\
% jude 01:23
and some save,
\\
\tab{}
snatching them out of the fire with fear,
\\
\tab{}
hating even the clothing stained by the flesh.

\newpage\section{Now to Him Who is Able}

% jude 01:24
Now to him who is able
\\
\tab{}
to keep them from stumbling,
\\
\tab{}
and to present you faultless
\\
\tab{}
\tab{}
before the presence of his glory
\\
\tab{}
\tab{}
\tab{}
in great joy,
\\
% jude 01:25
to God our Savior,
\\
\tab{}
who alone is wise,
\\
\tab{}
\tab{}
be glory and majesty,
\\
\tab{}
\tab{}
dominion and power,
\\
\tab{}
\tab{}
both now and forever.
\\
Amen.

