\chapter{2John}

\newpage\section{The Elder}

% 2john 01:01
The elder,
\\
to the chosen lady and her children,
\\
whom I love in truth,
\\
and not I only,
\\
but also all those who know the truth,
\\
% 2john 01:02
for the truth's sake,
\\
which remains in us,
\\
and it will be with us forever:

% 2john 01:03
Grace, mercy, and peace will be with us,
\\
from God the Father and from the Lord Jesus Christ,
\\
the Son of the Father,
\\
in truth and love.

\newpage\section{I Rejoice Greatly}

% 2john 01:04
I rejoice greatly that I have found some of your children walking in truth,
\\
even as we have been commanded by the Father.

\newpage\section{Now I Beg You, Dear Lady}

% 2john 01:05
Now I beg you, dear lady,
\\
not as though I wrote to you a new commandment,
\\
but that which we had from the beginning,
\\
that we love one another.

% 2john 01:06
This is love,
\\
that we should walk according to his commandments.

This is the commandment,
\\
even as you heard from the beginning,
\\
that you should walk in it.

\newpage\section{For Many Deceivers}

% 2john 01:07
For many deceivers have gone out into the world,
\\
those who don’t confess that Jesus Christ came in the flesh.

This is the deceiver and the Antichrist.

\newpage\section{Watch Yourselves}

% 2john 01:08
Watch yourselves,
\\
that we don’t lose the things which we have accomplished,
\\
but that we receive a full reward.

\newpage\section{Whoever Transgresses}

% 2john 01:09
Whoever transgresses and doesn’t remain in the teaching of Christ doesn’t have God.

He who remains in the teaching has both the Father and the Son.

% 2john 01:10
If anyone comes to you and doesn’t bring this teaching,
\\
don’t receive him into your house,
\\
and don’t welcome him,
\\
% 2john 01:11
for he who welcomes him participates in his evil deeds.

\newpage\section{Having Many Things to Write to You}

% 2john 01:12
Having many things to write to you,
\\
I don’t want to do so with paper and ink,
\\
but I hope to come to you and to speak face to face,
\\
that our joy may be made full.

% 2john 01:13
The children of your chosen sister greet you.

Amen.
