\chapter{3John}

\newpage\section{The Elder to Gaius the Beloved}

% 3john 01:01
The elder

to Gaius the beloved,
\\
\tab{}
whom I love in truth.

\newpage\section{Beloved}

% 3john 01:02
Beloved,
\\
I pray
\\
\tab{}
that you may prosper in all things
\\
\tab{}
and be healthy,
\\
\tab{}
\tab{}
even as your soul prospers.

% 3john 01:03
For I rejoiced greatly
\\
\tab{}
when brothers came
\\
\tab{}
and testified about your truth,
\\
\tab{}
\tab{}
even as you walk in truth.

% 3john 01:04
I have no greater joy than this:
\\
\tab{}
to hear about my children walking in truth.

\newpage\section{Beloved}

% 3john 01:05
Beloved,
\\
you do a faithful work
\\
\tab{}
in whatever you accomplish
\\
\tab{}
\tab{}
for those who are brothers and strangers.

% 3john 01:06
They have testified about your love
\\
\tab{}
before the assembly.

You will do well
\\
\tab{}
to send them forward
\\
\tab{}
\tab{}
on their journey
\\
\tab{}
\tab{}
\tab{}
in a way worthy of God,
\\
% 3john 01:07
because
\\
\tab{}
for the sake of the Name
\\
\tab{}
\tab{}
they went out,
\\
\tab{}
\tab{}
\tab{}
taking nothing from the Gentiles.

% 3john 01:08
We therefore ought to receive such,
\\
that we may be fellow workers
\\
\tab{}
for the truth.

\newpage\section{I Wrote to the Assembly}

% 3john 01:09
I wrote to the assembly,
\\
but Diotrephes,
\\
\tab{}
who loves to be first among them,
\\
doesn’t accept what we say.

% 3john 01:10
Therefore,
\\
if I come,
\\
I will call attention to his deeds which he does,
\\
\tab{}
unjustly accusing us with wicked words.

Not content with this,
\\
\tab{}
he doesn’t receive the brothers himself,
\\
\tab{}
and those who would,
\\
\tab{}
\tab{}
he forbids and throws out of the assembly.

\newpage\section{Beloved, Don’t Imitate That Which is Evil}

% 3john 01:11
Beloved,
\\
don’t imitate that which is evil,
\\
but that which is good.

He who does good is of God.

He who does evil hasn’t seen God.

\newpage\section{Demetrius Has the Testimony of All}

% 3john 01:12
Demetrius has the testimony of all,
\\
and of the truth itself;
\\
yes,
\\
we also testify,
\\
and you know that our testimony is true.

\newpage\section{I Had Many Things to Write to You}

% 3john 01:13
I had many things to write to you,
\\
but I am unwilling to write to you with ink and pen;
\\
% 3john 01:14
but I hope to see you soon.

Then we will speak face to face.

\newpage\section{Peace Be to You}

Peace be to you.

The friends greet you.

Greet the friends by name.
